### 2016-04-26 rscripts/location_clusters.Rmd
updates to drawing scripts

```{r, echo=FALSE, include=FALSE}
req.packages <- c("data.table", "ggplot2", "reshape2", "grid", "scales", "lubridate", "movMF")
need.pkgs <- req.packages[!sapply(req.packages, require, character.only = T)]
if (length(need.pkgs) != 0) install.packages(need.pkgs, dependencies = T)
source("munging.R")
source("pca_plots.R")
```

@@

```{r, echo=FALSE}
max_hours <- 24
min_logins <- 2;    min_users <- 6 # 6 user min remove abberant location
min_lifetime <- 30; min_loc_lifetime <- 30 # days
censor.dt <- loadCensored(
  raw.dt = loadRaw(),
  max_hours = max_hours, min_logins = min_logins, min_lifetime = min_lifetime,
  min_users = min_users, min_loc_lifetime = min_loc_lifetime
)
censor.dt
set.seed(0); training_portion <- .8
unique_locations <- censor.dt[,unique(location_id)]
training_locations <- sort(sample(
  unique_locations,
  size = length(unique_locations)*training_portion, replace = F
))
# ggplot(censor.dt[,list(usage=sum(logout-login)/60/60), by=list(location_id, year, month)]) + aes(x=month, y=usage, group=location_id) + facet_grid(year ~ .) + geom_line(alpha=0.5)
# users that qualify as regular:
# censor.dt[,list(lifetime = max(logout)-min(login)), by=list(location_id, user_id)][lifetime > 60*60*24*365, unique(user_id)]
```

@@

```{r, echo=F, fig.cap="Raw proportions by hour"}
ggplot(temporal_data_slice) + theme_bw() + aes(group = location_id, x = hour, y = value) + facet_grid(measure ~ .) + geom_line(alpha=0.2) + scale_x_discrete(breaks=0:23, expand=c(0,0)) +
  scale_y_continuous("proportion", expand=c(0,0))
```

```{r, echo=F, fig.cap="Measure Peak distribution"}
peaks <- temporal_data_slice[, list(peak=which.max(value)-1), by=list(location_id, measure)]
ggplot(peaks) + theme_bw() + aes(x = peak) + facet_grid(measure ~ .) + geom_bar(binwidth=1)
```

@@

ggplot(pwr[,
  list(power=value, frequency=as.numeric(sub("_perday","", variable))), by=list(location_id, measure)
]) + theme_bw() + aes(y = power, x=frequency, group=location_id) + facet_grid(measure ~ .) + geom_line(alpha=0.2) + scale_x_continuous("per day frequency", breaks=c(1,2,3,4,6,8,12))
# pwr[, list(peak_freq = variable[which.max(value)]), by=list(location_id, measure)][,.N,by=list(measure, peak_freq)]
```

@@

```{r, echo=F, fig.cap="Login, Logout, Usage Peak Clusters"}
ggplot(peaks[temporal_cluster]) + theme_bw() + aes(x = peak, fill=vMFcluster) + facet_grid(measure ~ .) + geom_bar(binwidth=1) + labs(fill="von Mises-Fisher\n3-Sphere\nCluster\nPeak Time")
```

@@

```{r, echo=F, fig.cap="Frequency Power Clusters"}
setkey(pwr, measure, location_id, variable)
peak_freq_cat <- pwr[,list(peak_freq = ifelse(variable[which.max(value)] == "1_perday","daily","multimode")), keyby=list(measure, location_id)]
tot_pwr <- pwr[,list(tot_pwr = sum(value)), keyby=list(measure, location_id)]
pwr_divisions <- tot_pwr[,{
  res <- as.list(quantile(tot_pwr, probs = c(1,2)/3))
  names(res) <- c("low","hi")
  res
}, keyby=measure]
pwr_cluster <- tot_pwr[pwr_divisions][peak_freq_cat][,
  list(peak_freq, pwr_cat = ifelse(tot_pwr < low,"lo",ifelse(tot_pwr < hi, "med","hi"))),
  keyby=list(measure, location_id)
]
ggplot(pwr[pwr_cluster][,
  list(power=value, frequency=as.numeric(sub("_perday","", variable)), peak_freq, pwr_cat),
  by=list(location_id, measure)
]) + theme_bw() + aes(y = power, x=frequency, group=location_id, alpha=peak_freq, color = pwr_cat) + facet_grid(measure ~ .) + geom_line() + scale_x_continuous("per day frequency", breaks=c(1,2,3,4,6,8,12))
```

@@

Finally, we can look at the relative usage per user:
\newpage\blandscape
```{r, echo=F, fig.width=11.25, fig.height=7, fig.cap="Locations clustered excess usage per user."}
agg.dt <- initial_digest$raw[,list(log10_total_duration,log10_unique_users,log10_lifetime), keyby=location_id]
lg10lm <- lm(log10_total_duration-log10_unique_users ~ log10_lifetime, agg.dt)
agg.dt <- cbind(agg.dt, predict(lg10lm, agg.dt, interval="prediction", level=1/3))[,
  lifetime_cat := factor(ifelse(log10_total_duration-log10_unique_users < lwr, "low",
                  ifelse(log10_total_duration-log10_unique_users < upr, "mid", "high")), levels=c("low","mid","high"), ordered=T)
][reduced_pwr_clust][temporal_cluster]
p <- ggplot(agg.dt) + theme_bw() +
  aes(y = log10_total_duration-log10_unique_users, x = log10_lifetime, color = vMFcluster, size = pwr_clust, alpha = pwr_clust) +
  with(agg.dt, annotate("ribbon", x=log10_lifetime, ymax=upr, ymin=lwr, fill="lightgrey")) +
  geom_vline(xintercept=log10(365*24*60*60), color="grey") +
  annotate("text", x=log10(365*24*60*60)+c(-0.02,0.02), y=5.75, label=c("< 1 year","> 1 year"), angle=90, color="grey") +
  geom_point() +
#  geom_ribbon(aes(ymax=upr, ymin=lwr, y=NULL, color=NULL, size=NULL), alpha=0.2) +
  labs(
    x = expression(log[10]("lifetime")),
    y = expression(log[10]*bgroup("(",frac("total usage","# unique users"),")")),
    color = "von Mises-Fisher\nPeak Time\nCluster"
  ) + scale_size_manual("power\ncluster", limits=c("low","med","hi"), values=c(2,5,8)) +
  scale_alpha_manual("power\ncluster", limits=c("low","med","hi"), values=(2^0.5)/c(2,5,8)^0.5)
p
```
\elandscape\newpage

\newpage\blandscape
```{r, echo=F, fig.width=11.25, fig.height=7, fig.cap="Raw proportions by hour"}
setkey(pwr_cluster, location_id, measure)
ggplot(temporal_data_slice[temporal_cluster][pwr_cluster]) + theme_bw() +
  aes(group = location_id, x = hour, y = value, color=pwr_cat) +
  facet_grid(measure ~ vMFcluster) + geom_line(alpha=0.3) +
  scale_x_discrete(breaks=0:23, expand=c(0,0)) +
  scale_y_continuous("proportion", expand=c(0,0))
```
\elandscape\newpage

@@

\newpage\blandscape
```{r, echo=F, fig.width=11.25, fig.height=7, fig.cap="distribution of main location type usage"}
digests <- rbind(
  lifetime_dts$digest[,list(switch_rate = switches/usage, main, share, type="usage")],
  pwr_dts$digest[,list(switch_rate = switches/usage, main, share, type="power")],
  vMF_dts$digest[,list(switch_rate = switches/usage, main, share, type="peaktime")]
)
ggplot(digests) + facet_grid(type ~ .) + theme_bw() + aes(x=log10(switch_rate), fill=main, alpha=factor(floor(share*10))) + geom_bar(binwidth=0.1) + scale_alpha_manual(breaks=0:10, values=seq(0.5,1,length.out = 11))
```
\elandscape\newpage

\newpage\blandscape
```{r, echo=F, fig.width=11.25, fig.height=7, fig.cap="normalized distribution of main location type usage"}
ggplot(digests) + facet_grid(type ~ .) + theme_bw() + aes(x=log10(switch_rate), fill=main, alpha=factor(floor(share*10))) + geom_bar(binwidth=0.1, position="fill") + scale_alpha_manual(breaks=0:10, values=seq(0.5,1,length.out = 11))
```
\elandscape\newpage

\newpage\blandscape
```{r, echo=F, fig.width=11.25, fig.height=7, fig.cap="user categorization, by primary location type utilization"}
plot_ref <- ref[
  lifetime_dts$digest[, list(lifetime_main = main, lifetime_share = share), keyby=user_id]
][
  pwr_dts$digest[, list(pwr_main = main, pwr_share = share), keyby=user_id]
][
  vMF_dts$digest[, list(peak_main = main, peak_share = share), keyby=user_id]
]
user_src.dt <- plot_ref[between(life, 365*24*60*60, 3*365*24*60*60) & between(ul,3,20)]
saveRDS(user_src.dt, "../input/user.RData")
#thing[, list(user_id, mains=interaction(lifetime_main, pwr_main, peak_main))][,.N,by=mains]
ggplot(user_src.dt[, list(y=log10(usage), x=log10(life), pwr_main, lifetime_main, peak_main, membership = lifetime_share * pwr_share * peak_share)]) +facet_grid(pwr_main ~ lifetime_main, labeller = function(var, val){
  if (var == "pwr_main") {
    ifelse(val == "lo", "smooth usage", ifelse(val=="med","some usage variability","highly variable usage"))
  } else {
    ifelse(val == "low", "low usage per time", ifelse(val=="mid","typical usage per time","high usage per time"))
  }
}) + aes(x=x,y=y, color=factor(peak_main), alpha = membership) + geom_point() + theme_bw() + labs(y="log(usage)", x="log(life)", color="usage\npeak")
```
\elandscape\newpage

@@

@@

>>>>

```{r, loadpkgs, echo=FALSE, include=FALSE}
req.packages <- c("data.table", "ggplot2", "reshape2", "grid", "scales", "lubridate", "movMF")
need.pkgs <- req.packages[!sapply(req.packages, require, character.only = T)]
if (length(need.pkgs) != 0) install.packages(need.pkgs, dependencies = T)
source("munging.R")
source("pca_plots.R")
```

@@

```{r, loadData, echo=FALSE}
max_hours <- 24
min_logins <- 2;    min_users <- 6 # 6 user min remove abberant location
min_lifetime <- 30; min_loc_lifetime <- 30 # days
censor.dt <- loadCensored(
  raw.dt = loadRaw(),
  max_hours = max_hours, min_logins = min_logins, min_lifetime = min_lifetime,
  min_users = min_users, min_loc_lifetime = min_loc_lifetime
)
censor.dt
set.seed(0); training_portion <- .8
unique_locations <- censor.dt[,unique(location_id)]
training_locations <- sort(sample(
  unique_locations,
  size = length(unique_locations)*training_portion, replace = F
))
# ggplot(censor.dt[,list(usage=sum(logout-login)/60/60), by=list(location_id, year, month)]) + aes(x=month, y=usage, group=location_id) + facet_grid(year ~ .) + geom_line(alpha=0.5)
# users that qualify as regular:
# censor.dt[,list(lifetime = max(logout)-min(login)), by=list(location_id, user_id)][lifetime > 60*60*24*365, unique(user_id)]
```

Let's look at some quick views of some components of the data.  First, how many hotspots are in use?  We can look at the life of all hotspots:

```{r, location_counts, echo=F, fig.cap="Location Counts"}
loclifetimes <- censor.dt[,
  list(start=min(login), end=max(logout)),
  keyby=location_id
]
p <- ggplot(loclifetimes) + theme_bw() + aes(y=location_id, yend=location_id, x=start/3600/24, xend=end/3600/24) + geom_segment(alpha=0.5) + labs(x="start / end day", y="location") + scale_x_continuous(breaks=(0:6)*365)
ggsave("location-liftimes.png", p, width=7, height=4)
p
```

as well as the net count of locations over time:

```{r, location_counts, echo=F, fig.cap="Location Counts"}
locCounts <- melt.data.table(loclifetimes, id.vars = "location_id")[,
  list(change=sum(c(1,-1)[variable])), keyby=value
]
p <- ggplot(locCounts[,list(time=value/3600/24, net=cumsum(change))][net>0]) + theme_bw() + aes(x=time, y=net) + geom_step() + coord_cartesian(xlim=c(1,2000), ylim=c(1,300), expand = F) + scale_y_log10("net locations", breaks=c(1,2,5,10,20,50,100,200)) + scale_x_continuous(breaks=(0:6)*365)
ggsave("location-net.png", p, width=7, height=4)
p
```

There's a similar trend in users:

```{r, location_counts, echo=F, fig.cap="Location Counts"}
userCounts <- melt.data.table(lifetimes <- censor.dt[,
  list(start=min(login), end=max(logout)),
  keyby=user_id
], id.vars = "user_id")[,
  list(change=sum(c(1,-1)[variable])), keyby=value
]
p <- ggplot(userCounts[,list(time=value/3600/24, net=cumsum(change))][net>0]) + theme_bw() + aes(x=time, y=net) + geom_step() + coord_cartesian(xlim=c(1,2000), ylim=c(1,20000), expand = F) + scale_x_continuous(breaks=(0:6)*365) + scale_y_log10("net users", breaks=c(1,2,5,10,20,50,100,200,500,1000,2000,5000,10000,20000))
ggsave("user-net.png", p, width=7, height=4)
p
```

@@

```{r, echo=F, fig.cap="Raw proportions by hour"}
p <- ggplot(temporal_data_slice) + theme_bw() + aes(group = location_id, x = hour, y = value) + facet_grid(measure ~ .) + geom_line(alpha=0.2) + scale_x_discrete(breaks=0:23, expand=c(0,0)) +
  scale_y_continuous("proportion", expand=c(0,0))
ggsave("time-sig.png", p, width=7, height=4)
p
```

```{r, echo=F, fig.cap="Measure Peak distribution"}
peaks <- temporal_data_slice[, list(peak=which.max(value)-1), by=list(location_id, measure)]
p <- ggplot(peaks) + theme_bw() + aes(x = peak) + facet_grid(measure ~ .) +
  geom_bar() +
  scale_x_discrete("peak hour", limits=0:23)
p
```

@@

p <- ggplot(pwr[,
  list(power=value, frequency=as.numeric(sub("_perday","", variable))), by=list(location_id, measure)
]) + theme_bw() + aes(y = power, x=frequency, group=location_id) + facet_grid(measure ~ .) + geom_line(alpha=0.2) + scale_x_continuous("per day frequency", breaks=c(1,2,3,4,6,8,12))
# pwr[, list(peak_freq = variable[which.max(value)]), by=list(location_id, measure)][,.N,by=list(measure, peak_freq)]
p
```

@@

```{r, echo=F, fig.cap="Login, Logout, Usage Peak Clusters"}
p <- ggplot(peaks[temporal_cluster]) + theme_bw() + aes(x = peak, fill=vMFcluster) + facet_grid(measure ~ .) + geom_bar(binwidth=1) + labs(fill="von Mises-Fisher\n3-Sphere\nCluster\nPeak Time")
ggsave("time-peaks.png", p, width=7, height=4)
p
```

@@

```{r, echo=F, fig.cap="Frequency Power Clusters"}
setkey(pwr, measure, location_id, variable)
peak_freq_cat <- pwr[,list(peak_freq = ifelse(variable[which.max(value)] == "1_perday","daily","multimode")), keyby=list(measure, location_id)]
tot_pwr <- pwr[,list(tot_pwr = sum(value)), keyby=list(measure, location_id)]
pwr_divisions <- tot_pwr[,{
  res <- as.list(quantile(tot_pwr, probs = c(1,2)/3))
  names(res) <- c("low","hi")
  res
}, keyby=measure]
pwr_cluster <- tot_pwr[pwr_divisions][peak_freq_cat][,
  list(peak_freq, pwr_cat = ifelse(tot_pwr < low,"lo",ifelse(tot_pwr < hi, "med","hi"))),
  keyby=list(measure, location_id)
]
p <- ggplot(pwr[pwr_cluster][,
  list(power=value, frequency=as.numeric(sub("_perday","", variable)), peak_freq, pwr_cat),
  by=list(location_id, measure)
]) + theme_bw() + aes(y = power, x=frequency, group=location_id, alpha=peak_freq, color = pwr_cat) + facet_grid(measure ~ .) + geom_line() + scale_x_continuous("per day frequency", breaks=c(1,2,3,4,6,8,12))
ggsave("freq-powers.png", p, width=7, height=4)
p
```

@@

Finally, we can look at the relative usage per user:
\newpage\blandscape
```{r, echo=F, fig.width=11.25, fig.height=7, fig.cap="Locations clustered excess usage per user."}
agg.dt <- initial_digest$raw[,list(log10_total_duration,log10_unique_users,log10_lifetime), keyby=location_id]
lg10lm <- lm(log10_total_duration-log10_unique_users ~ log10_lifetime, agg.dt)
agg.dt <- cbind(agg.dt, predict(lg10lm, agg.dt, interval="prediction", level=1/3))[,
  lifetime_cat := factor(ifelse(log10_total_duration-log10_unique_users < lwr, "low",
                  ifelse(log10_total_duration-log10_unique_users < upr, "mid", "high")), levels=c("low","mid","high"), ordered=T)
][reduced_pwr_clust][temporal_cluster]
p <- ggplot(agg.dt) + theme_bw() +
  aes(y = log10_total_duration-log10_unique_users, x = log10_lifetime, color = vMFcluster, size = pwr_clust, alpha = pwr_clust) +
  with(agg.dt, annotate("ribbon", x=log10_lifetime, ymax=upr, ymin=lwr, fill="lightgrey")) +
  geom_vline(xintercept=log10(365*24*60*60), color="grey") +
  annotate("text", x=log10(365*24*60*60)+c(-0.02,0.02), y=5.75, label=c("< 1 year","> 1 year"), angle=90, color="grey") +
  geom_point() +
#  geom_ribbon(aes(ymax=upr, ymin=lwr, y=NULL, color=NULL, size=NULL), alpha=0.2) +
  labs(
    x = expression(log[10]("lifetime")),
    y = expression(log[10]*bgroup("(",frac("total usage","# unique users"),")")),
    color = "von Mises-Fisher\nPeak Time\nCluster"
  ) + scale_size_manual("power\ncluster", limits=c("low","med","hi"), values=c(2,5,8)) +
  scale_alpha_manual("power\ncluster", limits=c("low","med","hi"), values=(2^0.5)/c(2,5,8)^0.5)
ggsave("locationclusters.png", p, width=7, height=4)
p
```
\elandscape\newpage

\newpage\blandscape
```{r, echo=F, fig.width=11.25, fig.height=7, fig.cap="Raw proportions by hour"}
setkey(pwr_cluster, location_id, measure)
p <- ggplot(temporal_data_slice[temporal_cluster][pwr_cluster]) + theme_bw() +
  aes(group = location_id, x = hour, y = value, color=pwr_cat) +
  facet_grid(measure ~ vMFcluster) + geom_line(alpha=0.3) +
  scale_x_discrete(breaks=0:23, expand=c(0,0)) +
  scale_y_continuous("proportion", expand=c(0,0))
p
```
\elandscape\newpage

@@

\newpage\blandscape
```{r, echo=F, fig.width=11.25, fig.height=7, fig.cap="distribution of main location type usage"}
digests <- rbind(
  lifetime_dts$digest[,list(switch_rate = switches/usage, main, share, type="usage")],
  pwr_dts$digest[,list(switch_rate = switches/usage, main, share, type="power")],
  vMF_dts$digest[,list(switch_rate = switches/usage, main, share, type="peaktime")]
)
p <- ggplot(digests) + facet_grid(type ~ .) + theme_bw() + aes(x=log10(switch_rate), fill=main, alpha=factor(floor(share*10))) + geom_bar(binwidth=0.1) + scale_alpha_manual(breaks=0:10, values=seq(0.5,1,length.out = 11))
p
```
\elandscape\newpage

\newpage\blandscape
```{r, echo=F, fig.width=11.25, fig.height=7, fig.cap="normalized distribution of main location type usage"}
p <- ggplot(digests) + facet_grid(type ~ .) + theme_bw() + aes(x=log10(switch_rate), fill=main, alpha=factor(floor(share*10))) + geom_bar(binwidth=0.1, position="fill") + scale_alpha_manual(breaks=0:10, values=seq(0.5,1,length.out = 11))
p
```
\elandscape\newpage

\newpage\blandscape
```{r, echo=F, fig.width=11.25, fig.height=7, fig.cap="user categorization, by primary location type utilization"}
plot_ref <- ref[
  lifetime_dts$digest[, list(lifetime_main = main, lifetime_share = share), keyby=user_id]
][
  pwr_dts$digest[, list(pwr_main = main, pwr_share = share), keyby=user_id]
][
  vMF_dts$digest[, list(peak_main = main, peak_share = share), keyby=user_id]
]
user_src.dt <- plot_ref[between(life, 365*24*60*60, 3*365*24*60*60) & between(ul,3,20)]
saveRDS(user_src.dt, "../input/user.RData")
#thing[, list(user_id, mains=interaction(lifetime_main, pwr_main, peak_main))][,.N,by=mains]
p <- ggplot(user_src.dt[, list(y=log10(usage), x=log10(life), pwr_main, lifetime_main, peak_main, membership = lifetime_share * pwr_share * peak_share)]) +facet_grid(pwr_main ~ lifetime_main, labeller = function(vardt){
  if (!is.null(vardt$pwr_main)) {
    list(c(lo="smooth usage",med="some usage variability",hi="highly variable usage")[as.character(vardt$pwr_main)])
  } else {
    list(c(low="low usage per time", mid="typical usage per time",high="high usage per time")[as.character(vardt[[1]])])
  }
}) + aes(x=x,y=y, color=factor(peak_main), alpha = membership) + geom_point() + theme_bw() + labs(y="log(usage)", x="log(life)", color="usage\npeak")
ggsave("users.png", p)
p
```
\elandscape\newpage

@@

```{r}
slice <- user_src.dt[lifetime_main=="mid" & pwr_main == "med" & peak_main == "middle"]
mlt.slice <- melt.data.table(slice[,list(life,ulog=log10(usage), unilocs=ul),by=user_id], id.vars = "user_id", measure.vars = c("life","ulog","unilocs"))
ggsave("mmm_life.png", ggplot(mlt.slice[variable == "life"]) + theme_bw() + aes(x=value, y=..density..) + geom_histogram() + labs(x="lifetime (end - start)", y="density"), width=7, height=4)
ggsave("mmm_usage.png", ggplot(mlt.slice[variable == "ulog"]) + theme_bw() + aes(x=value, y=..density..) + geom_histogram() + labs(x="log10(usage)", y="density"), width=7, height=4)
ggsave("mmm_ulocs.png", ggplot(mlt.slice[variable == "unilocs"]) + theme_bw() + aes(x=value, y=..density..) + geom_histogram() + labs(x="unique locations", y="density"), width=7, height=4)

slice <- user_src.dt[lifetime_main=="mid" & pwr_main == "lo" & peak_main == "early"]
mlt.slice <- melt.data.table(slice[,list(life,ulog=log10(usage), unilocs=ul),by=user_id], id.vars = "user_id", measure.vars = c("life","ulog","unilocs"))
ggsave("mle_life.png", ggplot(mlt.slice[variable == "life"]) + theme_bw() + aes(x=value, y=..density..) + geom_histogram() + labs(x="lifetime (end - start)", y="density"), width=7, height=4)
ggsave("mle_usage.png", ggplot(mlt.slice[variable == "ulog"]) + theme_bw() + aes(x=value, y=..density..) + geom_histogram() + labs(x="log10(usage)", y="density"), width=7, height=4)
ggsave("mle_ulocs.png", ggplot(mlt.slice[variable == "unilocs"]) + theme_bw() + aes(x=value, y=..density..) + geom_histogram() + labs(x="unique locations", y="density"), width=7, height=4)
```

```{r}
mmm.cc <- loclifetimes[setkey(fread("../../muri-overall/output/matched/mid/med/middle/10/001-covert-0-cc.csv", col.names = c("user.a","user.b","location_id","start","end","other")), location_id)][start < i.end & i.start < end, list(start=i.start, end=i.end, user.a, user.b, location_id)]
mmm.cu <- loclifetimes[setkey(fread("../../muri-overall/output/matched/mid/med/middle/10/001-covert-0-cu.csv", col.names = c("user.a","user.b","location_id","start","end","other")), location_id)][start < i.end & i.start < end, list(start=i.start, end=i.end, user.a, user.b, location_id)]
mmm.all <- rbind(mmm.cc, mmm.cu)
mmm.both <- rbind(
  mmm.all[user.a < 0, list(mx=max(end),mn=min(start),sm=sum(end-start),ul=length(unique(location_id))), by=list(user_id=user.a)],
  mmm.all[user.b < 0, list(mx=max(end),mn=min(start),sm=sum(end-start),ul=length(unique(location_id))), by=list(user_id=user.b)]
)[,list(life=max(mx)-min(mn), usage=sum(sm), ul=sum(ul)),by=user_id]
```

```{r}
mle.cc <- loclifetimes[setkey(fread("../../muri-overall/output/matched/mid/lo/late/10/001-covert-0-cc.csv", col.names = c("user.a","user.b","location_id","start","end","other")), location_id)][start < i.end & i.start < end, list(start=i.start, end=i.end, user.a, user.b, location_id)]
mle.cu <- loclifetimes[setkey(fread("../../muri-overall/output/matched/mid/lo/late/10/001-covert-0-cu.csv", col.names = c("user.a","user.b","location_id","start","end","other")), location_id)][start < i.end & i.start < end, list(start=i.start, end=i.end, user.a, user.b, location_id)]
mle.all <- rbind(mle.cc, mle.cu)
mle.both <- rbind(
  mle.all[user.a < 0, list(mx=max(end),mn=min(start),sm=sum(end-start),ul=length(unique(location_id))), by=list(user_id=user.a)],
  mle.all[user.b < 0, list(mx=max(end),mn=min(start),sm=sum(end-start),ul=length(unique(location_id))), by=list(user_id=user.b)]
)[,list(life=max(mx)-min(mn), usage=sum(sm), ul=sum(ul)),by=user_id]
```

@@

group sizes 5-20 by 5, also a 30
meeting frequency - once a week, once every two weeks, once every month
try
 - meeting at less probable times
 - meeting location be inconsistent with normal behavior

detection based on cycles
